Robust background subtraction in traffic environments

### 2019-02-22 paper/Paper.tex
Added final revision of the paper. Updated readme and sources to run the algorithm.

To change the decision treshold $R(x_i)$ is saved an array of recently observed pixel values in the background model $B(x_i)$, we also create an array $\mathbf{D}(x_i) = \{D_1(x_i ),...,D_N(x_i)\}$ of minimal decision distances. Whenever an update of $B_k(x_i)$ is carried out, the currently observed minimal distance:

@@

(second) dynamic controller for $T(x_i)$ following the assumption that pixels are mostly wrongly classified as foreground in areas of high dynamic background the strength of the adjustment in the controller can be adapted using the dynamic estimator $\overline{d}_{min}(x_i)$. So can be defined:

>>>>

To change the decision treshold $R(x_i)$ is saved an array of recently observed pixel values in the background model $B(x_i)$. We also create an array $\mathbf{D}(x_i) = \{D_1(x_i ),...,D_N(x_i)\}$ of minimal decision distances. Whenever an update of $B_k(x_i)$ is carried out, the currently observed minimal distance:

@@

(second) dynamic controller for $T(x_i)$ following the assumption that pixels are mostly wrongly classified as foreground in areas of high dynamic background. The strength of the adjustment in the controller can be adapted using the dynamic estimator $\overline{d}_{min}(x_i)$. So can be defined:
